Fluent statistical computing interfaces for biological data analysis

### 2020-07-29 index.Rmd
update toc; rebuild
add lay summary

---
title: 'Fluent statistical computing interfaces for biological data analysis'
author: 'Stuart Lee'
degreetype: 'Doctor of Philosophy'
site: bookdown::bookdown_site
degrees: 'B.MatComSci., University of Adelaide; MSc.Bioinformatics. University of Melbourne'
bibliography: [bib/plyranges.bib, bib/fluentGenomics.bib, bib/thesisrefs.bib]
link-citations: yes
---

@@

This is the website for my PhD thesis at Monash University (Australia), titled "Fluent statistical computing interfaces for biological data analysis". 
It is a work in progress.

>>>>

---
title: 'Fluent statistical computing interfaces for biological data analysis'
author: 'Stuart Lee'
degreetype: 'Doctor of Philosophy'
site: bookdown::bookdown_site
degrees: 'B.MatComSci., University of Adelaide; MSc.Bioinformatics. University of Melbourne'
bibliography: [bib/plyranges.bib, bib/fluentGenomics.bib, bib/superintronic.bib, bib/liminal.bib, bib/thesisrefs.bib]
link-citations: yes
---

@@

This work contributes new computing interfaces for the analysis of data 
collected from technologies that measure changes in biology, like gene 
expression. The first interface is a new tool that unites data measured along
the genome under a common language of transformation. This interface enables
analysts to interpret and combine multiple results from different technologies
in a clear and simple way. The second interface provides a framework for 
identifying interesting regions along the genome. The third interface empowers
analysts to interrogate complex models using visual diagnostics. All 
are provided as open source software packages.
